15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
fix the worst line breaks

    \end{itemize}
    \item Divisions with quantifiers:
    \begin{itemize}
      \item Equality\\
Logics: UF, UFDT
\item Equality+LinearArith\\
Logics: ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
\item Equality+MachineArith\\
Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, AUFBV, AUFBVFP,
AUFBVDTLIA, UFBV, UFBVFP, UFBVLIA
\item Equality+NonLinearArith\\
Logics: ANIA, AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA, UFNRA
\item Arith\\
Logics: LRA, LIA, NIA, NRA
\item Bitvec\\
Logics: BV
\item FPArith\\
Logics: BVFP, FP, BVFPLRA, FPLRA
    \end{itemize}
  \end{itemize}

@@

  \item {\bf \mvaltrack.}  Last year's competition introduced the experimental
  divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
  track.  This year, the divisions containing these logics will no longer be
  experimental.  In addition, we will add this year new experimental divisions
  QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
  QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
  QF\_UFBV benchmarks).

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_LinearIntArith, QF\_LinearRealArith, QF\_Equality (only with QF\_UF
benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
%
This year all divisions with UF logics (with uninterpreted functions) are
experimental divisions.
%
The track will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.

>>>>

    \end{itemize}
    \item Divisions with quantifiers:
    \begin{itemize}
      \item Equality\\
Logics: UF, UFDT
\item Equality+LinearArith\\
Logics: \sloppy ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
\item Equality+MachineArith\\
Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, AUFBV, AUFBVFP,
AUFBVDTLIA, UFBV, UFBVFP, UFBVLIA
\item Equality+NonLinearArith\\
Logics: ANIA, AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA, UFNRA
\item Arith\\
Logics: LRA, LIA, NIA, NRA
\item Bitvec\\
Logics: BV
\item FPArith\\
Logics: BVFP, FP, BVFPLRA, FPLRA
    \end{itemize}
  \end{itemize}

@@

  \item {\bf \mvaltrack.}  \emergencystretch.5cm Last year's competition introduced the experimental
  divisions QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA in the model validation
  track.  This year, the divisions containing these logics will no longer be
  experimental.  In addition, we will add this year new experimental divisions
  QF\_Equality (only with QF\_UF benchmarks), QF\_Equality+LinearArith (only with
  QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with
  QF\_UFBV benchmarks).

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_LinearIntArith, QF\_LinearReal\-Arith, QF\_Equality (only with QF\_UF
benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
%
This year all divisions with UF logics (with uninterpreted functions) are
experimental divisions.
%
The track will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.
